Score-based tests of measurement invariance: Use in practice

### 2013-10-29 frontiers/frontiers.Rnw
slightly rephrased discussion of direction usage of ordL2BB
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@289 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

Finally, if the user anticipates multiple calculations of the
$\max\mathit{LM}_o$ statistic for a specific dataset, it is possible
to save time by simulating critical values once and re-using them for
multiple tests.  We can use the \code{ordL2BB()} command to generate
critical values, then obtain the test statistic in the usual manner.
<<ordsave, eval=FALSE>>=
## Simulate critical values
mLMo <- ordL2BB(yg$agegroup)
## Use these critical values for the test
maxlmo <- sctest(restr, order.by = yg$agegroup, parm = 1:4,
  vcov = "info", functional = mLMo)
@ 
The \code{ordL2BB()} command automatically generates critical values
for testing 1 to 20 parameters at a time, with critical values for
greater numbers of parameters being obtained through the optional
argument \code{nproc}.  One can re-use \code{mLMo} in this manner for
further tests of the youth gratitude data.  Critical values must be
resimulated for new data, however, because they depend on the
proportion of individuals observed at each level of the ordinal
variable (see~\eqref{eq:maxlmo}).

>>>>

Finally, if the user anticipates multiple calculations of the
$\max\mathit{LM}_o$ statistic for a specific dataset, it is possible
to save time by simulating critical values once and re-using them for
multiple tests.  We can use the \code{ordL2BB()} command to generate
critical values and store them in an object \code{mLMo}, say.
Then, this object can be employed to obtain the test statistic in the usual manner.
<<ordsave, eval=FALSE>>=
mLMo <- ordL2BB(yg$agegroup)
maxlmo <- sctest(restr, order.by = yg$agegroup, parm = 1:4,
  vcov = "info", functional = mLMo)
@ 
The \code{ordL2BB()} command automatically generates critical values
for testing 1 to 20 parameters at a time. If only a smaller number
of parameters (e.g., only up to 6) is to be tested, some computation time can be
saved by setting the \code{nproc} argument accordingly (e.g., \code{nproc = 1:6}).
In the same way, \code{nproc} can be employed to simulate higher-dimensional
fluctuation processes suitable for testing more parameters. One can re-use
\code{mLMo} in this manner for further tests of the youth gratitude data.
Critical values must be resimulated for new data, however, because they depend on the
proportion of individuals observed at each level of the ordinal
variable (denoted $t_\ell$ for Equation~\eqref{eq:maxlmo}).
